---
title: "About"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(jsonlite)
library(gt)
professors_list <- fromJSON("./professor_ratings_by_college.json")
salaries <- read_csv("./college-salaries/salaries-by-college-type-reduced.csv")

nth_prof <- function(n) {
  
  college_name <- professors_list[n] %>% as_tibble() %>% colnames()
  
  # To avoid errors, separate out the cases where there is and 
  # where there is not data on professor ratings, includes
  # a row of NA values for colleges with no data
  
  if (length(professors_list[[n]]) >= 1) {
    return(professors_list[n] %>% as_tibble() %>% pull(1) %>% mutate(college = college_name))
  } else {
    return(
        tibble(
          name = c(NA_character_), 
          rating = c(NA_integer_), 
          difficulty = c(NA_integer_), 
          department = c(NA_character_), 
          college = c(college_name)
        )
      )
  }
}

professors = nth_prof(1)
for (ind in 1:length(professors_list)) {
  if (!is.null(nth_prof(ind))) {
    professors <- professors %>% union(nth_prof(ind))
  }
}
professors
```

## The Project
In this project, I explore the ratings of professors on campuses across America. All the code for data collection and analysis can be found
on my academic [github](https://github.com/jonah-harvard/college-scraping). In this project, I look to determine if the distribution of ratings differs from college to college. I also look to see if the distribution of ratings correlates at all with the median salary of graduates of the college.

## The Data
The data that I am working with concern the ratings of professors across different colleges, and the median salaries of graduates of those colleges.

#### Rating Data
I wrote a [script in python](https://github.com/jonah-harvard/college-scraping/blob/master/scrape_rate_my_professor.py),
that I use to collect professor rating data from [Rate My Professor](https://www.ratemyprofessors.com/). Some thought should be put in to whether 
the ratings are truly representative of the general student opinion of these teachers and readers should just keep in mind that it represents ratings as reported in this specific context. The first 10 professors (alphabetically) are shown below: 
```{r professors}
professors %>% 
  select("Name"=name, "Rating"=rating, "Difficulty"=difficulty, "Department" = department, "College" = college) %>% 
  arrange(Name) %>% tail(-1) %>% head(10) %>% gt() %>% 
  tab_header(
    title = "Professor Ratings"
  )
```

#### Salary Data
The data on median salaries after graduation comes from [Kaggle](https://www.kaggle.com/wsj/college-salaries) and was released by the Wall Street Journal. The data feature the median salary of graduates just after graduating and the median salary of graduates well into their careers. Below are the first 10 colleges.

```{r salaries}
salaries %>% head(10) %>%  gt() %>% 
  tab_header(
    title = "Median Salaries by College"
  )
```


```{r graphing, warning=FALSE}
professors <- professors %>% na.omit()
professors %>% 
  ggplot(aes(difficulty, rating, color = department)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(group = college)) +
  labs(
    title = "Rating as a Function of Difficulty by College",
    x = "Difficulty",
    y = "Rating"
  ) + 
  theme_classic() + 
  theme(legend.position = "none") + 
  facet_wrap(~college) 
```

```{r distributions}
histogram_of_college <- function(college_name) {
  college_data <- professors %>% filter(college == college_name)
  print(cor.test(college_data$difficulty, college_data$rating))
  college_data %>% ggplot(aes(rating)) + geom_histogram()
}

professors %>% ggplot(aes(rating)) + geom_histogram() + labs(title = "Rating by College") + facet_wrap(~ college)
professors %>% ggplot(aes(difficulty)) + geom_histogram() + labs(title = "Difficulty by College") + facet_wrap(~ college)
```
