---
title: "Initial Analysis and Exploration of Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(jsonlite)
library(gt)
professors_list <- fromJSON("./professor_ratings_by_college.json")
salaries <- read_csv("./college-salaries/salaries-by-college-type-reduced.csv")

nth_prof <- function(n) {
  
  college_name <- professors_list[n] %>% as_tibble() %>% colnames()
  
  # To avoid errors, separate out the cases where there is and 
  # where there is not data on professor ratings, includes
  # a row of NA values for colleges with no data
  
  if (length(professors_list[[n]]) >= 1) {
    return(professors_list[n] %>% as_tibble() %>% pull(1) %>% mutate(college = college_name))
  } else {
    return(
        tibble(
          name = c(NA_character_), 
          rating = c(NA_integer_), 
          difficulty = c(NA_integer_), 
          department = c(NA_character_), 
          college = c(college_name)
        )
      )
  }
}

professors = nth_prof(1)
for (ind in 1:length(professors_list)) {
  if (!is.null(nth_prof(ind))) {
    
    # Rolling together each of the tibbles into one, containing all professor data
    
    professors <- professors %>% union(nth_prof(ind))
  }
}
professors
```

# Relationships

```{r graphing, warning=FALSE}
professors <- professors %>% na.omit()

professors %>% 
  ggplot(aes(difficulty, rating)) + 
  geom_point() +
  labs(
    title = "Rating as a Function of Difficulty",
    x = "Difficulty",
    y = "Rating"
  ) + 
  theme_classic()
```

The initial graphing of the data doesn't seem to convey much. By all appearances, there could be very little correlation between difficulty and rating.

```{r graphing_by_college}
professors %>% 
  ggplot(aes(difficulty, rating, color = department)) + 
  geom_point() + 
  
  # Use geom_smooth to accentuate the relationship between variables
  
  geom_smooth(method = "lm", aes(group = college)) +
  labs(
    title = "Rating as a Function of Difficulty by College",
    x = "Difficulty",
    y = "Rating"
  ) + 
  theme_classic() + 
  theme(legend.position = "none") + 
  facet_wrap(~college) 
```

When faceting by college, however, it becomes a lot clearer that there is, in fact, a negative correlation between difficulty and rating.

# Distributions

```{r distributions, message=FALSE}

# histogram_of_college is a simple function for looking at the data
# associated with a particular college.

histogram_of_college <- function(college_name) {
  college_data <- professors %>% filter(college == college_name)
  print(cor.test(college_data$difficulty, college_data$rating))
  college_data %>% ggplot(aes(rating)) + geom_histogram()
}

professors %>% ggplot(aes(rating)) + geom_histogram() + labs(title = "Rating by College") #+ facet_wrap(~ college)
professors %>% ggplot(aes(difficulty)) + geom_histogram() + labs(title = "Difficulty by College") #+ facet_wrap(~ college)
```


When looking at the distribution of difficulties, as one might expect, the data seems more or less normally distributed, with mean 3. On the other hand, however, ratings are skewed strongly to the left.

