---
title: "College Professors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jsonlite)
professors_list <- fromJSON("./professor_ratings_by_college.json")

nth_prof <- function(n) {
  if (length(professors_list[n]) >= 1) {
    return(professors_list[n] %>% as_tibble() %>% pull(1) %>% mutate(college = professors_list[n] %>% as_tibble() %>% colnames()))
  } else {
    return(
        tibble(
          name = c(NA), 
          rating = c(NA), 
          difficulty = c(NA), 
          department = c(NA), 
          college = c(professors_list[n] %>% as_tibble() %>% colnames())
        )
      )
  }
}

professors = nth_prof(1)
for (ind in 1:10){#length(professors_list)) {
  if (!is.null(nth_prof(ind))) {
    professors <- professors %>% union(nth_prof(ind))
  }
}
professors
```

# Data

The data that I am working with concern the ratings of professors across different colleges, and the median salaries of graduates of those colleges.

The ratings data I scraped from the popular site Rate My Professor. Below is an example of the data scraped.
```{r professors}
professors %>% head(50) %>% select(-difficulty)
```
The salary data I got from Kaggle. The dataset was released by the Wall Street Journal.
```{r salaries}
salaries <- read_csv("./college-salaries/salaries-by-college-type-reduced.csv")
salaries
```


I intend to use this data to explore both the differences in distribution of ratings and the relationship between ratings and salary after graduation.
